Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-20 snapshot_system/failover.tex
Added VM failure

>>>>

The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failue}.
The graph assumes 10X40GB snapshots per VM with 20\% unique data after local
dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
VM).

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		title={Node failure affect on VMs},
		xlabel={Number of nodes failed},
		ylabel={chance that a VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		]
		\addplot[color=blue,mark=*] table{figures/vm_failure.txt};
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}
